SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-20 paper/bio_MTedit.tex
example fixed

\begin{example}
%
In figure~\ref{fig:M1}, we present a VTS that has 3 compartments and 8 molecules, and a corresponding pairing matrix. Molecules are numbered 0-7. In the VTS, labels are a string of molecule ids, and an overline over a an id indicates that the molecule is active. This VTS is an example of one where every molecule on the node is active, and the activity of the molecules on the edges are controlled by presence of the other molecules. On the right side of the figure, we show the pairing matrix. An entry 1 represents pairing between molecules; $\times$ represents no pairing. Rows are labels on vesicles, columns are labels on compartments. Every molecule flows on a cycle, ensuring steady state. This is a 3-connected graph.
\end{example}
%--------------------- DO NOT ERASE BELOW THIS LINE --------------------------

>>>>

\begin{example}
%
In figure~\ref{fig:M1}, we present a VTS that has 3 compartments and 8 molecules, and a corresponding pairing matrix.
%
Molecules are numbered 0-7.
%
In the VTS, labels are a string of molecule ids, and an overline over an id indicates that the molecule is active.
%
Every molecule on the node is active.
%
The activity of the molecules on an edge are controlled
by presence of the other molecules on the edge.
%
On the right side of the figure, we show the pairing matrix.
%
An entry 1 represents pairing between molecules.
%
$\times$ represents no pairing.
%
Rows corresponds to the labels of edges, and
columns corresponds to the labels of nodes.
%
Every molecule flows on a cycle, ensuring steady state.
%
This is a 3-connected graph.
\end{example}
%--------------------- DO NOT ERASE BELOW THIS LINE --------------------------
